\section{Welch t-test Analysis}
This section uses Welch t-tests and Mann-Whitney U (MWU) tests to determine if the mean contributions and stochastic dominance differ between groups.

\subsection{Founder against Late Joiner (Table 1)}
\begin{itemize}
    \item \textbf{Key Finding}: Founders generally touch more architectural components (Packages, Classes, and Methods) than Late Joiners during their initial commit phases.
    \item \textbf{Statistical Significance}: For the first 20 commits, the difference in Classes touched is significant ($p = 0.0001$), with a Welch Statistic of $4.06$.
\end{itemize}

\subsection{Moderate against Sustained (Table 2)}
\begin{itemize}
    \item \textbf{Key Finding}: Moderate developers exhibit a higher mean of unique components touched in their early commits compared to Sustained developers.
    \item \textbf{Statistical Significance}: All comparisons for Packages, Classes, and Methods are highly significant ($p = 0.0000$), with Welch Statistics ranging from $3.41$ to $15.18$.
\end{itemize}

\subsection{Moderate Founder against Moderate Late Joiner (Table 3)}
\begin{itemize}
    \item \textbf{Key Finding}: Within the Moderate category, Founders engage with significantly more Classes and Methods than Late Joiners.
    \item \textbf{Data Point}: For the first 20 commits, Moderate Founders touch an average of $86.22$ classes compared to $36.22$ for Late Joiners ($p = 0.0022$).
\end{itemize}

\subsection{Sustained Founder against Sustained Late Joiner (Table 4)}
\begin{itemize}
    \item \textbf{Key Finding}: Among Sustained contributors, Founders also demonstrate a broader exploration of the codebase than Late Joiners.
    \item \textbf{Data Point}: At 20 commits, Sustained Founders touch a mean of $401.24$ methods, while Late Joiners touch $126.41$ ($p = 0.0036$).
\end{itemize}

\section{ANOVA Generate Analysis}
The Two-Way ANOVA evaluates the influence of Role (Founder vs. Late Joiner) and Category (Tenure) on architectural engagement.

\subsection{Analysis Including Transient Developers (Table 5)}
\begin{itemize}
    \item \textbf{Main Effects}: Both Role and Category show significant effects on the number of Classes and Methods touched ($p < 0.05$).
    \item \textbf{Interaction}: Significant interaction effects were found, suggesting that the impact of being a Founder varies depending on the developer's eventual tenure category.
\end{itemize}

\subsection{Analysis Excluding Transient Developers (Table 6)}
\begin{itemize}
    \item \textbf{Findings}: When Transients are removed, the Role (Founder vs. Late Joiner) remains a statistically significant factor for Classes and Methods ($p < 0.05$). 
    \item \textbf{Shift}: The Category effect (Moderate vs. Sustained) often loses significance for Packages and specific Class/Method thresholds when only established contributors are considered.
\end{itemize}

\section{Key Observations from Pairwise Comparisons}
The Tukey HSD results clarify the interactions identified in the ANOVA. Notably, for class exploration at 20 commits, significant differences persist between:
\begin{itemize}
    \item \textbf{Role within Tenure}: Founder Sustained developers touch significantly more classes than Late Joiner Sustained developers (Adj P = 0.0467).
    \item \textbf{Tenure within Role}: Late Joiner Moderate developers touch significantly more classes than Late Joiner Sustained developers (Adj P = 0.0005).
    \item \textbf{Transient Disparity}: Comparisons against both Founder and Late Joiner Transients show the most extreme mean differences, confirming their limited architectural engagement.
\end{itemize}

\section{Strategy Logistic Regression}
The logistic regression model identifies early-stage predictors for a developer becoming a "Sustained" contributor.

\begin{itemize}
    \item \textbf{Intercept}: Consistently negative intercepts (e.g., $-2.6487$ to $-3.9773$) indicate that the baseline probability of becoming Sustained is low without active engagement.
    \item \textbf{Odds Ratios ($e^{\beta}$)}: All Odds Ratios for component counts are greater than $1.0$. For example, each additional package touched in the first 5 commits increases the odds of being sustained by $7.37\%$ ($OR = 1.0737$).
    \item \textbf{Predictive Threshold}: To reach a $50\%$ probability of being a Sustained contributor, the model suggests a threshold of approximately $146$ classes touched within the first 5 commits.
\end{itemize}

\section{Summary of Whole Findings}
The data demonstrates that \textbf{project entry timing} (Founder status) is a primary driver of codebase exploration, with Founders consistently touching more unique components than Late Joiners across all tenure categories. While \textbf{Moderate} developers show high levels of initial exploration, the \textbf{Logistic Regression} model confirms that the breadth of early architectural engagement (touching more Packages, Classes, and Methods) is a statistically significant indicator of whether a developer will eventually transition into a \textbf{Sustained} contributor.
